Bayesian Restricted Likelihood Methods: Conditioning on Insufficient Statistics in Bayesian Regression\thanksref{T1}

### 2018-11-09 revision_1/response.tex

\item I found the discussion how the suggested approach is related to ABC methods very vague and would appreciate more details.
\begin{itemize}
\item We have provide more details.
\end{itemize}

\item  There are several references to unpublished material such as Jung et al. (2014) which makes it hard to evaluate the value added by the corresponding material in the present paper.
\begin{itemize}
\item 
\end{itemize}

\item As for ABC methods, the suggested approach heavily relies on choosing appropriate statistics of the data. Since robustness to ``bad” data is the major concern of the authors, they should pursue one reviewer’s advice go beyond M-estimators and consider high-break down estimators such as LMS and LTS. Also the choice of a suitable statistic for the scale is an important issue that should be discussed in more detail.
\begin{itemize}
\item We agree that the choice of statistic is paramount and doesn't have to be restricted to M-estimation. We included two simple examples utilizing LMS and LTS. And added dialogue of the choice of statistic to the discussion. 
\end{itemize}

\item  As noted by one referee, the gain in performance of the suggested approach for the two models discussed in the paper is not terribly convincing. Hence, I strongly encourage the authors to include an additional example that shows a significant edge of their method over classical ones, or at least to provide artificial data, where this is the case.
\begin{itemize}
\item We have added a simulation study showing the enhance performance of our method in a situation where the data generating model is known. We have also made some refinements to the data analysis section to help highlight some of the advantages of out approach. In particular, we present results for individual state-level regressions for states of various sizes. We also streamline the presentation of the hierarchical model by including a single training sample size, as the differences before were not that meaningful with the different training sample sizes. 
\end{itemize}

@@

\newpage

\section*{Comments from Referee 1}
Major Points:
The writing in this paper is very smooth; it reads easily. This is good but I’m worried this is achieved by not providing enough detail and reasoning. Hence the bulk of my comments below are efforts to quantify what further details the authors almost certainly know and would be well advised to include.
\begin{enumerate}
\item The Introduction and Sec. 2 are too long and detract from the focus of the paper: The authors basically want to give (3) and two examples of it, namely (1) and (2). Then they want to explain how they generate $(y|T (y), \theta)$. The central idea is strong enough to stand on its own without the elaborate discussion. The discussion points seem more appropriate for a concluding section on the conceptual implications of using a restricted likelihood. I suggest this because the conceptual implications are not the focus of the paper, they result from the methodology. The discussion material in the early part of the paper could be moved to the last section and made more focused. There are also a good number of references that the authors might want to read and possibly cite in the general area of model uncertainty outside the across-model prior setting. In no particular order, some are: Zhu, Ibrahim, Tang 2011 BKA, Barnardo and Smith 2000 (for M-closed, complete, and open), Gustafson and Clarke 2004 CJS, Clarke 2010 BA, Draper 1996 JRSSB, Yuan and Clarke 1999 CJS, Clyde and Iverson 2013 (M-open, proceedings volume) and Clarke, Clarke and Yu 2013 (M-complete) BA.

\begin{itemize}
\item We have re-organized and shortened Sections 1 and 2 and moved some of the commentary to the discussion. Several of the suggested references were added in the introduction.
\end{itemize}

2) The paper should be more self-contained: Even after several readings I do not understand the procedure on p. 12 satisfactorily. Details are left out, e.g., how (7) follows from (8); the one sentence explanation on l. 8-9 is not enough. Why is it OK to drop the conditioning on $T (y_{p}) = T (y_{c}) = T (y_{obs})$? Some notation seems odd e.g., what is the relationship amongst yp, yc, and yobs? Where is the expression p(·)? Or do the authors mean p(·|?)? Also, I thought the idea of Metropolis-Hastings was to generate a sample from a distribution for which direct generation was difficult. If evaluation of $f(y|\theta)$ is straighforward (as stated on p. 12, l. 10) and $f(y|T (y), \theta)$ is available, why is the author’s procedure important? I think the answer is that the authors want to compare $f(y|\theta)$ to the use of a $f(T(y)|\theta)$ corrected by an estimate of $f(y|T(y),\theta)$ so that one can use the authors procedure without having $f(y|\theta)$ but this should be stated explicitly.
A related point is that the discussion in Sec. 3.2.1 was also hard to follow because too many details were left out. The role of z? needs to be explained better. While the words in the last two lines of p. 12 may be obvious to those who know the methodology, giving the mathematical formalities and the motivations for the various steps would make them and p. 13, 14 easier to follow. In particular, where does y? come from? Why would one want to transform y? into y as in Theorem 1? How does the expression in Theorem 1 lead to the set in (9)? I have no doubts that the authors can provide more formality and motivation for each step in the procedure; it’s just a matter of doing it.
\begin{itemize}
\item We have made substantial revisions to the paper, especially the MH algorithm in an attempt to make the details more clear including: more detail on the simplification of the the MH ratio R in (7) and (8); the fact that  $f(y|T (y), \theta)$ is not available in closed form (only up to a proportionality constant), so direct generation is difficult.
\end{itemize}

@@

3) The intuition should be better explicated: The authors have clearly thought carefully about the intuition behind their procedure, but some how it doesn’t 2 come across in Figs. 1 and 2 which I am unable to link to the formalities they do present. The authors have not yet found a good way to express their ideas so that they can be readily assimilated by some one who does not already understand. I don’t understand the steps in the reasoning in Sec. 3.2.2. It’s OK to relegate proofs to an Appendix, but the reasoning should be clearer in the main text.
\begin{itemize}
\item We agree that this section was difficult to follow. We have made substantial effort to re-organize the section and explain the steps and reasonings more clearly. 
\end{itemize}

4) The results for the application need better labeling/exposition: It would be helpful if the authors could write out exactly and explicitly what cross-validation type of evaluation is being calculated. This is described at the bottom of p. 24, top of p. 25 in words, but the mathematical expressions should be given fully as well. This would clarify the role of the base method and the comment on p. 27, l. 3-4. The same sort of comment applies to p. 27-28: Please give the mathematical expressions rather than just the words. (This would make the last lines on p. 29 easier to follow.) Maybe it’s just the way that my copy printed, but in Figs. 3, 4, and 5 the ranges/dots are hard to distinguish from each other so it’s hard to tell which is what. Could the different cases have different symbols that would be easier to tell apart? Even making the figures larger would help. To make it easier for the reader could the discussion of Table 1 p. 31 refer to the rows in the table? That would make it easier for the reader to tell which comparisons the discussion was commenting on. A related question: What does Fig. 1 show that is essential to the discussion?

\begin{itemize}
\item The results sections has been refined substantially. The models were simplified and more focused to elucidate some of the advantages of our method. A more complete description with mathematical expressions is provided for how the TLM is calculated. We paid more attention to the clarity of the new figures. The purpose of Figure 1 (now Figure 3) is explained better in Section on the MCMC algorithm (now section 4).
\end{itemize}

### 2018-11-09 revision_1/paper.tex
edits bug fix for data analysis section

The data are grouped by states with a varying number of agencies by state. Identifiers such as agency/agent names are removed. Likewise, state labels and agency types (identifying the varying contractual agreements) have been made generic to protect the proprietary nature of the data.

@@

As an exploratory view, a plot of the square root of household count in 2012, against that in 2010 

@@

\begin{figure}[t]
\centering
\includegraphics[width=5in]{scatter_by_state.png}
\caption{The square root of count in 2012 versus that in 2010 for four states. The colors represent the varying contractual agreements as they stood in 2010 (`Type').  Agencies that closed during the 2010-2012 period are represented by the zero counts for 2012.}
\label{fig:ctVct}
\end{figure}

@@

\subsubsection{Comparison of predictive performance}
%Model performance is assessed using the mean and standard deviation of the TLM 
%across $K = 50$ different splits into training and holdout samples. 
`Type 1' agencies are of special interest to the company and so the evaluation of the TLM is done on only holdout samples of `Type 1', wheres the training is done on agencies of all types. This is intended to demonstrate the robustness properties of the various methods. 
%First, we include all observations
%in each validation sample to calculate TLM for each split. We then
%repeat the evaluation using only certain subsets of the validation
%sample that are of special interest. Subsets include open agencies,
%open `Type 1' agencies, and `Type 1' agencies. For brevity, we include
%results for the `Type 1' agencies only. As noted, assessing model
%predictions on this set of agencies is of special interest to the
%company.  A range of training sample sizes was used and we include
%results from $n=25,100,1000,$ and $2000$ out of a total of $3180$ agencies. 
%The trimming fraction, $\alpha$, ranges from $0$ to $0.3$. A classical robust regression to the prior data assigns zero weight to around $16\%$ of observations; in essence removing these from the analysis. This informed the range of trimming fractions chosen.  
%In practice, we would set $\alpha$ slightly larger than $0.16$.  
Models are fit to four states labelled State 2, 15, 27, and 36, with $n = 222, 40, 117,$ and $46$, representing a range of sample sizes. Fitting is done on $K = 50$ training/holdout samples with training sample sizes taken to be $.25n$ and $0.50n$. Holdout evaluation is done on the remaining (`Type 1') samples. For the data augmentation MCMC step under the restricted likelihood models, the acceptance rates range from  $0.15$ to $0.76$ across the states, repetitions, and two versions of the model. The average $TLM_b(A)$ over the $K = 50$ training/holdout samples for the four states and seven methods are shown in Figure \ref{fig:tlm} where the base model is the Student-t model and $\alpha = 0.3$. Similar results are observed for other base models, with this one being most advantageous to the Student-t model. The error-bars are plus/minus one standard deviation of the average $TLM_b(A)$ over the $K = 50$  training/holdout samples. It is clear the normal Bayesian model used as the full model (Normal) and the classical ordinary least squares fits (OLS) have poor performance due to the significant amount of outlier contamination in the data. In comparing our restricted methods to their corresponding classical methods, there is small, but consistent improvement across the states and training sample size. For state 2, the largest state with $n = 222$, the restricted and classical robust methods have similar performance especially for larger training sample size. This reflects the diminishing effect of the prior as the sample size grows. Notably, the Student-t model performs poorly in comparison for this state. The predictive distribution explicitly accounts for heavy-tailed values, resulting in poorer predictions of the `good` data (i.e., the Type 1 agencies). Likewise, for State 27, another larger state, the Student-t model is outperformed by our restricted methods.   For the other states, the Student-t performs similarly to our restricted methods for the smaller states (State 15 and 36) and smaller training sample size (25\% of the sample). However, the performance is worse for the larger training sample size (50\% of the sample). Intuitively, as more data is available for fitting, more outliers appear and the heavy-tailed model compensates for them by assuming they come from the tails of the model which is detrimental for prediction. The relative performance of the models are similar for various values of $\alpha$ as seen in Figure \ref{fig:tlmbyAlpha} which shows results for training sample size $0.5n$.

@@

The average over states, $\overline{TLM}_b(A)_{\cdot}= \frac{1}{22} \sum_{j =1}^{22} TLM_b(A)_{j}$ for each of the $K$ repetitions is summarized in Figure
\ref{fig:hierTLM} for several trimming fractions using the Student-t as the base model. The points are the average of the $\overline{TLM}_b(A)_{\cdot}$ over the $K$ repetitions with errorbars plus/minus one standard deviation over $K$. The normal theory fits, both Bayesian and classical, perform poorly and are left out of the figures. As the trimming fraction used for the TLM increases, so does TLM since more outliers are being trimmed. Similar patterns were seen in the individual state level regressions in Section \ref{regModelNW}. Despite being used as the base model to compute TLM, the Student-t doesn't perform well in comparison to the robust regressions. We attribute this to the assumption of heavier tails resulting in smaller log marginal values on average; emphasizing again that the t-model will do well to discount outlying observations but doesn't provide a natural mechanism for only predicting `good' (i.e. non-outlying) data. On average, the classical robust regressions fit separately within each state slightly outperform the restricted likelihood hierarchical models. The hierarchical model does however reduce variance in predictions at the cost of an increase in bias induced by the prior distributions. This can be seen in Figure \ref{fig:hierTLMsd} which shows the standard deviation of $\overline{TLM}_b(A)_{\cdot}$ relative to the mean over the $K=50$ repetitions. It is clear that the hierarchical model reduces sample-to-sample variation in comparison to the classical robust model counterparts.

@@

\begin{figure}[t]
\centering
\includegraphics[width=6in]{hier_sd_tlm.png}
\caption{Hierarchical model results: standard deviation of $\overline{TLM}_b(A)_{\cdot}$ relative to the mean over $K = 50$ splits into training and holdout sets for several values of the trimming fraction $\alpha$. Results are given for the two restricted likelihood versions of the hierarchical model and their corresponding robust regression models fit separately within each state.}
\label{fig:hierTLMsd}
\end{figure}

It is also interesting to examine the results within each state. Figure \ref{fig:hierTLMstate} summarizes ${TLM}_b(A)_{j}$ for each state where the points and errorbars are the averages and plus/minus one standard deviation of ${TLM}_b(A)_{j}$ over the $K = 50$ repetitions. The results are only given for the models using Tukey's M-estimators since, in general, these models performed the best on average. This is attributed to the corresponding $\psi$-function used in the M-estimation which trims large outliers from the data completely. Huber's version down-weights outliers, but never completely trims them.  The states are ordered along the $x$-axis according to number of agencies within the state (shown in parentheses). In several of the smaller states, the restricted hierarchical model performs better on average with similar performance between the models in most of the larger states; a reflection of the decreased influence of the prior. It is clear that the prior is having the effect of pooling information across states; beneficial for reducing the sample-to-sample variance. Generally,  the standard deviations are smaller for the hierarchical model for smaller states with virtually identical standard deviations for the larger states. Similar benefits are often seen for hierarchical models \citep[e.g.,][]{gelman2006}.

@@

%This work describes the concept of conditioning on insufficient statistics in Bayesian models, a method we term the restricted likelihood. The examples demonstrate the potential predictive improvement over competing methods in outlier-prone settings where the conditioning statistic targets the mean of the non-outlying data (e.g. M-estimators). 
%Attempting to model outliers can be seen as a special case of  misspecification of the original model for the non-outlying data. The traditional view is that, if the model is inadequate, one should build a better model. In our empirical work, as data sets have become larger and more complex, we have bumped into settings where we cannot realistically build the perfect model. We ask the question Òby attempting to improve our model through elaboration, will the overall performance of the model suffer?Ó If yes, we avoid the elaboration, retaining a model with some level of misspecification. Acknowledging that the model is misspecified implies acknowledging that the sampling density is incorrect, exactly as we do when outliers are present. In this sense, misspecified models and outliers are reflections of the same phenomenon, and we see the restricted likelihood as a method for dealing with this problem. 
Many routine choices in an analysis react to the gap between reality and the
statistical model, where a bit of set-up work improves inferential
performance.  Often, these choices can be recast in the framework of
restricted likelihood presented here, lending them more formality and facilitating
development of theoretical results. A greater benefit of our framework is that it leads us to blend classical estimation with
Bayesian methods. Here, we concentrate on outlier-prone settings where natural choices for conditioning statistic are classical robust estimators targeting the mean of the non-outlying data (e.g., M-estimators).  The likelihood conditioned on these estimators is used to move from prior to posterior. The update follows Bayes' Theorem, conditioning on the observed estimators exactly.   Computation is driven by MCMC methods, requiring only a supplement to existing algorithms by adding a Gibbs step to sample from the space of data sets satisfying the observed statistic. This step has additional computation costs. The estimator must be computed at every iteration to propose a new $\by$. This cost, as well as the need to find orthonormal bases derived from gradients of the estimators, adds some computational time compared to the full likelihood MCMC. The cost of finding the bases can be driven down by an understanding of the geometric space from which the samples are drawn as described in Section~\ref{highDim}. Additionally, we have seen good mixing of the MCMC chains across a wide-variety of examples.

Outside of outlier-prone settings, we might condition on the results of a set of estimating equations, designed to enforce lexical preferences for those features of the analysis considered most important, yet still producing inferences for secondary aspects of the problem. For example, the computational strategies we devised here allow us to apply the method to inference on quantiles of a regression model by, for example, conditioning on estimates of these quantiles. This leads to questions regarding the choice of summary statistic to apply. For outliers, we have applied some obvious choices (M-estimators, LMS, LTS) which have shown value in classical robust estimation. Properties of such estimators are well known and can be used as a basis for selecting one. In general, great ingenuity has been used to create a wide variety of estimators designed to handle specific manifestations of a misspecified model; where outliers are just a specific case.  The estimators are typically accompanied by asymptotic results on consistency and distribution.  These results can be used as starting point for choosing appropriate statistics in specific settings. In general, we recommend a choice based on the analyst's understanding of the problem, model, reality, deficiencies in the model,  inferences to be made, and the relative importance of various inferences.  %In our words, to provide desirable inference, we recommend use of robust and relevant summary statistics in conjunction with Bayesian models.

%Many of these results carry over to our blend of classical and Bayesian methods, although regularity conditions differ.  We expect our procedures to have strong large sample performance, especially in settings where
%pooling of information is of value.

The most general setting, of which outliers are a subset, is model misspecification. The traditional view is that, if the model is inadequate, one should build a better model. In our empirical work, as data sets have become larger and more complex, we have bumped into settings where we cannot realistically build the perfect model. We ask the question ``by attempting to improve our model through elaboration, will the overall performance of the model suffer?'' If yes, we avoid the elaboration, retaining a model with some level of misspecification. Acknowledging that the model is misspecified implies acknowledging that the sampling density is incorrect, exactly as we do when outliers are present. In this sense, misspecified models and outliers are reflections of the same phenomenon, and we see the restricted likelihood as a method for dealing with this more general problem.

The framework allows us to retain many benefits of Bayesian methods:  it requires a complete model for the data; it lets us combine various sources of information both through the use of a prior distribution and through creation of a hierarchical model; it guarantees admissibility of our decision rules among the class based on the summary statistic $T(\by)$; and it naturally leads us to focus on predictive inference.  The work does open a number of questions open to further work, including a need to revisit such issues as model selection, model averaging for predictive performance, and the role of diagnostics.

@@

Finally, recall $\rho\sim\text{beta}(a_\rho,b_\rho)$ with mean $\mu_\rho=a_\rho/(a_\rho+b_\rho)$ given a beta prior and precision
$\psi_\rho=a_\rho+b_\rho$ given a gamma prior. There is little evidence of any strong correlation amongst estimates of $\sigma^{2}_{j}$ in the prior data set and we set the prior mean of $\mu_{\rho}$ equal to $0.2$ and prior variance to $.01$. Noting $\text{var}(\rho|\mu_{\rho}, \psi_{\rho})=\mu_{\rho} (1-\mu_{p})/(\psi_{\rho}+1)$ we plug in $\mu_{\rho} = 0.2$ and $\text{var}(\rho|\mu_{\rho}, \psi_{\rho}) = 0.01$. Solving for $\psi_{\rho}$ results in a value of $15$. This is taken to be the mean of the gamma prior on $\psi_{\rho}$. Finally, we  set the rate parameter for to 1 implying the variance of the gamma prior is equal to its the mean. With this specification, the prior on $\rho$ has 80\% of the central mass between roughly $0.03$ and $0.42$ and reflects our prior believe that there is likely only weak correlation amongst the $\sigma^{2}_{j}$'s.
%%The variance was set to twice the inverse Fisher information evaluated at $\hat\rho_{mle}$

>>>>

The data are grouped by states with a varying number of agencies by state. Identifiers such as agency/agent names are removed. Likewise, state labels and agency types (identifying the varying contractual agreements) have been made generic to protect the proprietary nature of the data. Additionally, the counts scaled to have standard deviation one before anlaysis. 

@@

As an exploratory view, a plot of the square root of (scaled) household count in 2012, against that in 2010 

@@

\begin{figure}[t]
\centering
\includegraphics[width=5in]{scatter_by_state.png}
\caption{The square root of (scaled) count in 2012 versus that in 2010 for four states. The colors represent the varying contractual agreements as they stood in 2010 (`Type').  Agencies that closed during the 2010-2012 period are represented by the zero counts for 2012.}
\label{fig:ctVct}
\end{figure}

@@

\subsubsection{Comparison of predictive performance}
%Model performance is assessed using the mean and standard deviation of the TLM 
%across $K = 50$ different splits into training and holdout samples. 
`Type 1' agencies are of special interest to the company and so the evaluation of the TLM is done on only holdout samples of `Type 1', wheres the training is done on agencies of all types. This is intended to demonstrate the robustness properties of the various methods. 
%First, we include all observations
%in each validation sample to calculate TLM for each split. We then
%repeat the evaluation using only certain subsets of the validation
%sample that are of special interest. Subsets include open agencies,
%open `Type 1' agencies, and `Type 1' agencies. For brevity, we include
%results for the `Type 1' agencies only. As noted, assessing model
%predictions on this set of agencies is of special interest to the
%company.  A range of training sample sizes was used and we include
%results from $n=25,100,1000,$ and $2000$ out of a total of $3180$ agencies. 
%The trimming fraction, $\alpha$, ranges from $0$ to $0.3$. A classical robust regression to the prior data assigns zero weight to around $16\%$ of observations; in essence removing these from the analysis. This informed the range of trimming fractions chosen.  
%In practice, we would set $\alpha$ slightly larger than $0.16$.  
Models are fit to four states labelled State 2, 15, 27, and 36, with $n = 222, 40, 117,$ and $46$, representing a range of sample sizes. Fitting is done on $K = 50$ training/holdout samples with training sample sizes taken to be $.25n$ and $0.50n$. Holdout evaluation is done on the remaining (`Type 1') samples. For the data augmentation MCMC step under the restricted likelihood models, the acceptance rates range from  $0.16$ to $0.76$ across the states, repetitions, and two versions of the model. The average $TLM_b(A)$ over the $K = 50$ training/holdout samples for the four states and seven methods are shown in Figure \ref{fig:tlm} where the base model is the Student-t model and $\alpha = 0.3$. Similar results are observed for other base models. The error-bars are plus/minus one standard deviation of the average $TLM_b(A)$ over the $K = 50$  training/holdout samples. It is clear the normal Bayesian model used as the full model (Normal) and the classical ordinary least squares fits (OLS) have poor performance due to the significant amount of outlier contamination in the data. In comparing our restricted methods to their corresponding classical methods, there is small, but consistent improvement across the states and training sample size. For state 2, the largest state with $n = 222$, the restricted and classical robust methods have similar performance especially for larger training sample size. This reflects the diminishing effect of the prior as the sample size grows. Notably, the Student-t model performs poorly in comparison for this state. The predictive distribution explicitly accounts for heavy-tailed values, resulting in poorer predictions of the `good' data (i.e., the Type 1 agencies). Likewise, for State 27, another larger state, the Student-t model is outperformed by our restricted methods.   For the other states (State 15 and 36), the Student-t performs similarly to our restricted methods for smaller training sample size (25\% of the sample). However, the performance is slightly worse for the larger training sample size (50\% of the sample). Intuitively, as more data is available for fitting, more outliers appear and the heavy-tailed model compensates for them by assuming they come from the tails of the model; an assumption which is detrimental for prediction. Comparisons of the models depend on $\alpha$ as seen in Figure \ref{fig:tlmbyAlpha} which shows results for different $\alpha$ for training sample size $0.5n$. For smaller $\alpha$ (in this case $\alpha = 0.1$), many outliers are left untrimmed resulting in lower TLM  for all methods and noticeably larger standard deviation for the classical robust methods and our restricted likelihood. Larger values of $\alpha$ ensure the predictive performance assessment excludes the majority of outliers. The proportion of $0$ counts in the data is roughly $0.14$, suggesting $\alpha$ should be at least this large.

@@

The average over states, $\overline{TLM}_b(A)_{\cdot}= \frac{1}{22} \sum_{j =1}^{22} TLM_b(A)_{j}$ for each of the $K$ repetitions is summarized in Figure
\ref{fig:hierTLM} for several trimming fractions using the Student-t as the base model. The points are the average of the $\overline{TLM}_b(A)_{\cdot}$ over the $K$ repetitions with errorbars plus/minus one standard deviation over $K$ with larger values representing better predictive performance. As the trimming fraction used for the TLM increases, so does TLM since more outliers are being trimmed. Similar patterns were seen in the individual state level regressions in Section \ref{regModelNW}. Despite being used as the base model to compute TLM, the Student-t doesn't perform well in comparison to the robust regressions. We attribute this to the assumption of heavier tails resulting in smaller log marginal values on average; emphasizing again that the t-model will do well to discount outlying observations but doesn't provide a natural mechanism for only predicting `good' (i.e. non-outlying) data. For each trimming fraction, our restricted likelihood hierarchical models outperform the classical robust regressions fit separately within each state. The hierarchical model also reduce variance in predictions resulting in smaller error bars. This improvement decreases with $\alpha$ but is still noticeable for $\alpha = 0.3$. Both the Tukey and Huber versions perform similarly.

@@

%\begin{figure}[t]
%\centering
%\includegraphics[width=6in]{hier_sd_tlm.png}
%\caption{Hierarchical model results: standard deviation of $\overline{TLM}_b(A)_{\cdot}$ relative to the mean over $K = 50$ splits into training and holdout sets for several values of the trimming fraction $\alpha$. Results are given for the two restricted likelihood versions of the hierarchical model and their corresponding robust regression models fit separately within each state.}
%\label{fig:hierTLMsd}
%\end{figure}

It is also interesting to examine the results within each state. Figure \ref{fig:hierTLMstate} summarizes ${TLM}_b(A)_{j}$ with $\alpha = 0.3$ for each state where the points and errorbars are the averages and plus/minus one standard deviation of ${TLM}_b(A)_{j}$ over the $K = 50$ repetitions. The results are only given for the models using Tukey's M-estimators (Huber's version looks similar). The states are ordered along the $x$-axis according to number of agencies within the state (shown in parentheses). In several of the smaller states, the restricted hierarchical model performs better with similar performance between the models in most of the larger states; a reflection of the decreased influence of the prior. It is clear the hierarchical structure is having the effect of pooling information across states; beneficial for improving performance in some of the smaller states. The standard deviations are smaller for the hierarchical model in smaller states with virtually identical standard deviations for the larger states. Similar benefits are often seen for hierarchical models \citep[e.g.,][]{gelman2006}.

@@

%This work describes the concept of conditioning on insufficient statistics in Bayesian models, a method we term the restricted likelihood. The examples demonstrate the potential predictive improvement over competing methods in outlier-prone settings where the conditioning statistic targets the mean of the non-outlying data (e.g. M-estimators). 
%Attempting to model outliers can be seen as a special case of  misspecification of the original model for the non-outlying data. The traditional view is that, if the model is inadequate, one should build a better model. In our empirical work, as data sets have become larger and more complex, we have bumped into settings where we cannot realistically build the perfect model. We ask the question Òby attempting to improve our model through elaboration, will the overall performance of the model suffer?Ó If yes, we avoid the elaboration, retaining a model with some level of misspecification. Acknowledging that the model is misspecified implies acknowledging that the sampling density is incorrect, exactly as we do when outliers are present. In this sense, misspecified models and outliers are reflections of the same phenomenon, and we see the restricted likelihood as a method for dealing with this problem. 
This paper discusses the restricted likelihood where posterior inference is conducted by conditioning on a summary statistic rather than the complete data. 
The framework leads us to blend classical estimation with Bayesian methods.
%Many routine choices in an analysis react to the gap between reality and the
%statistical model, where a bit of set-up work improves inferential
%performance.  Often, these choices can be recast in the framework of
%restricted likelihood presented here, lending them more formality and facilitating
%development of theoretical results. 
%A greater benefit of our framework is that it leads us to blend classical estimation with Bayesian methods. 
Here, we concentrate on outlier-prone settings where natural choices for conditioning statistic are classical robust estimators targeting the mean of the non-outlying data (e.g., M-estimators).  The likelihood conditioned on these estimators is used to move from prior to posterior. The update follows Bayes' Theorem, conditioning on the observed estimators exactly.   Computation is driven by MCMC methods, requiring only a supplement to existing algorithms by adding a Gibbs step to sample from the space of data sets satisfying the observed statistic. This step has additional computation costs driven by  the need to compute the estimator and an orthonormal basis derived from gradients of the estimator at each iteration. The cost of finding the basis can be driven down by an understanding of the geometric space from which the samples are drawn as described in Section~\ref{highDim}. Additionally, we have seen good mixing of the MCMC chains across a wide-variety of examples.

Outside of outlier-prone settings, we might condition on the results of a set of estimating equations, designed to enforce lexical preferences for those features of the analysis considered most important, yet still producing inferences for secondary aspects of the problem. For example, the computational strategies we devised here allow us to apply the method to inference on quantiles of a regression model by, for example, conditioning on estimates of these quantiles. This leads to questions regarding the choice of summary statistic to apply. For outliers, we have applied some obvious choices (M-estimators, LMS, LTS) which have shown value in classical robust estimation. Properties of such estimators are well known and can be used as a basis for selecting one. In general, great ingenuity has been used to create a wide variety of estimators designed to handle specific manifestations of a misspecified model; where outliers are just a specific case.  The estimators are typically accompanied by asymptotic results on consistency and distribution.  These results can be used as starting point for choosing appropriate statistics in specific settings. In general, we recommend a choice based on the analyst's understanding of the problem, model, reality, deficiencies in the model,  inferences to be made, and the relative importance of various inferences.

In general, this framework can be used to address model misspecification, of which the presence of outliers is an example. The traditional view is that, if the model is inadequate, one should build a better model. In our empirical work, as data sets have become larger and more complex, we have bumped into settings where we cannot realistically build the perfect model. We ask the question ``by attempting to improve our model through elaboration, will the overall performance of the model suffer?'' If yes, we avoid the elaboration, retaining a model with some level of misspecification. Acknowledging that the model is misspecified implies acknowledging that the sampling density is incorrect, exactly as we do when outliers are present. In this sense, misspecified models and outliers are reflections of the same phenomenon, and we see the restricted likelihood as a method for dealing with this more general problem. The framework allows us to retain many benefits of Bayesian methods:  it requires a complete model for the data; it lets us combine various sources of information both through the use of a prior distribution and through creation of a hierarchical model; it guarantees admissibility of our decision rules among the class based on the summary statistic $T(\by)$; and it naturally leads us to focus on predictive inference.  The work does open a number of questions for further work, including a need to revisit such issues as model selection, model averaging for predictive performance, and the role of diagnostics.

@@

Finally, recall $\rho\sim\text{beta}(a_\rho,b_\rho)$ with mean $\mu_\rho=a_\rho/(a_\rho+b_\rho)$ given a beta prior and precision
$\psi_\rho=a_\rho+b_\rho$ given a gamma prior. There is little evidence of any strong correlation amongst estimates of $\sigma^{2}_{j}$ in the prior data set and we set the prior mean of $\mu_{\rho}$ equal to $0.2$ and prior variance to $.01$. Noting $\text{var}(\rho|\mu_{\rho}, \psi_{\rho})=\mu_{\rho} (1-\mu_{p})/(\psi_{\rho}+1)$ we plug in $\mu_{\rho} = 0.2$ and $\text{var}(\rho|\mu_{\rho}, \psi_{\rho}) = 0.01$. Solving for $\psi_{\rho}$ results in a value of $15$. This is taken to be the mean of the gamma prior on $\psi_{\rho}$. Finally, we  set the rate parameter for to 1 implying the variance of the gamma prior is equal to its the mean. With this specification, the prior on $\rho$ has 80\% of the central mass between roughly $0.03$ and $0.42$ and reflects our prior belief that there is likely only weak positive correlation amongst the $\sigma^{2}_{j}$'s.
%%The variance was set to twice the inverse Fisher information evaluated at $\hat\rho_{mle}$
